Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-06-12 man/tables/t_sampled_plots.Rmd
update

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

clima <- read.csv(here::here("/data/climate_obsnev", "obsnev_qp_pop.csv"), header = TRUE)
cli <- clima %>% filter(pop %in% c(2,6)) %>% mutate_if(is.numeric, funs(round(., 1))) %>% 
  dplyr::select(pop, mean, variable) %>% 
  spread(variable, mean) %>% 
  mutate(name = case_when(
    pop == 2 ~ 'SJ',
    pop == 6 ~ 'CA-High'
  )) %>% dplyr::select(-pop)

# duplicate row for CA site
x <- cli[2,] 
x$name <- 'CA-Low'
cli <- cli %>% bind_rows(x) %>% 
  mutate_at(1, round, 0) %>% 
  unite(temp, c(tmin, tmax), sep=" - ")

t1raw <- t1raw %>% inner_join(cli, by='name')

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

@@

# clima <- read.csv(here::here("/data/climate_obsnev", "obsnev_qp_pop.csv"), header = TRUE)
# cli <- clima %>% filter(pop %in% c(2,6)) %>% mutate_if(is.numeric, funs(round(., 1))) %>% 
#   dplyr::select(pop, mean, variable) %>% 
#   spread(variable, mean) %>% 
#   mutate(name = case_when(
#     pop == 2 ~ 'SJ',
#     pop == 6 ~ 'CA-High'
#   )) %>% dplyr::select(-pop) 
# 
# # duplicate row for CA site
# x <- cli[2,] 
# x$name <- 'CA-Low'
# cli <- cli %>% bind_rows(x) %>% 
#   mutate_at(1, round, 0) %>% 
#   unite(temp, c(tmin, tmax), sep=" - ")

# Update use worlclim2 
clima <- read.csv(here::here("/data/climate_worldclim", "dendro_worldclim.csv"), header = TRUE)

clima <- clima %>% 
  mutate(site = case_when(
    site == 'SJHigh' ~ 'SJ', 
    site == 'SJLow' ~ 'SJ',  
    site == 'CAHigh' ~ 'CA-High',
    site == 'CALow' ~ 'CA-Low'
  )) %>% 
  mutate_at(2, round, 0) %>% 
  mutate_at(3:5, round, 1) %>% 
  group_by(site) %>% 
  summarise_each(mean) %>% 
  dplyr::select(name = site, prec = p, tmin, tmax) %>% 
  unite(temp, c(tmin, tmax), sep="-")

t1raw <- t1raw %>% inner_join(clima, by='name')
